Generalized Tractability

### 2023-04-23 GeneralizedTractability_230418.tex
Updates from Overleaf

Let $\{\cf_d\}_{d \in \naturals}$ and $\{\cg_d\}_{d \in \naturals}$ be sequences of Hilbert spaces, and $\{\SOL_d : \cf_d \to \cg_d\}_{d \in \naturals}$ be a sequence of linear solution operators  with adjoints $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
\begin{equation} \label{eq:eigenvalues}
\lambda_{\max}^2 \ge \lambda_{1,d}^2 \ge \lambda_{2,d}^2 \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots, \qquad d \in \naturals.
\end{equation}
This means that the non-negative $\lambda_{i,d}$ are the singular values of the operator $\SOL_d$. We remark that in the literature on Information-Based Complexity the singular values of $\SOL_d$ are often denoted by $\sqrt{\lambda_{i,d}}$ instead of $\lambda_{i,d}$. However, since we assume non-negativity of the $\lambda_{i,d}$, the notation used here is equivalent.  The non-decreasing ordering of the eigenvalues for each $d$ facilitates the proof of conditions for tractability, but our conditions do not depend on the ordering.

@@

@@

Note that this definition of sub-$h$-$T$ tractability implies that
\begin{equation} \label{eq:comp_slow_hcT}
		\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{h(cT(\varepsilon^{-1},d,\vp))} = 0 \qquad \forall c > 0,
\end{equation}
which means that for $\varepsilon \to 0$ or $d \to \infty$  $\comp(\varepsilon,d))$ must increase slower than $h(cT(\varepsilon^{-1},d,\vp))$, no matter how small $c$ is.

@@

\section{Summary}

\fred{Do we consider the case of normalized error?}

>>>>

Let $\{\cf_d\}_{d \in \naturals}$ and $\{\cg_d\}_{d \in \naturals}$ be sequences of Hilbert spaces, and $\{\SOL_d : \cf_d \to \cg_d\}_{d \in \naturals}$ be a sequence of linear solution operators  with adjoints $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
\begin{equation} \label{eq:eigenvalues}
\lambda_{\max}^2 \ge \lambda_{1,d}^2 \ge \lambda_{2,d}^2 \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots, \qquad d \in \naturals.
\end{equation}
\fred{Are we restricting ourselves by not allowing $\lambda_{1,d} \to \infty$ as $d \to \infty$}
This means that the non-negative $\lambda_{i,d}$ are the singular values of the operator $\SOL_d$. We remark that in the literature on Information-Based Complexity the singular values of $\SOL_d$ are often denoted by $\sqrt{\lambda_{i,d}}$ instead of $\lambda_{i,d}$. However, since we assume non-negativity of the $\lambda_{i,d}$, the notation used here is equivalent.  The non-decreasing ordering of the eigenvalues for each $d$ facilitates the proof of conditions for tractability, but our conditions do not depend on the ordering.

@@

\fred{Point out that $T$ could increase quite rapidly, but this does not affect our theorems.}

@@

Note that this definition of sub-$h$-$T$ tractability implies that
\begin{equation} \label{eq:comp_slow_hcT}
		\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{h(cT(\varepsilon^{-1},d,\vp))} = 0 \qquad \forall c > 0,
\end{equation}
which means that for $\varepsilon \to 0$ or $d \to \infty$  $\comp(\varepsilon,d)$ must increase slower than $h(cT(\varepsilon^{-1},d,\vp))$, no matter how small $c$ is.

@@

\section{Discussion and Summary}

\fred{
\begin{itemize}
\item Do we consider the case of normalized error? (Peter) 
\item Are there cases of $T$ that do not correspond to known tractability measures? (Kachi)
\item Restricted domain? (Fred)
\end{itemize}}
